Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
review Robust synthesis of Linear Systems

The problem of parametric control synthesis based on stability measures for
continous Linear Time Invariant (LTI) Single Input-Single Output (SISO)
systems has been researched for several decades.  On a theoretical level it
is a solved problem~\cite{wonham1967pole} for which researches continuously
seek better results based on a number of properties in addition to
stability.  A vast range of pole placement techniques such as Moore's
algorithm for eigenstructure assignment~\cite{klein1977eigenvalue} or the
more recent Linear Quadratic Regulator (LQR)~\cite{bemporad2002explicit}
have been used in several papers with increasing degrees of succes to ensure
stability.  The latter approach highlights the importance of conserving
energy during the control process, which results amongst other things in
lower running costs.  Since real systems are subject to tolerance and noise
as well as the need for economy, more recent works focus on the problems of
achieving robust stability with minimum
gain~\cite{schmid2014unified,konigorski2012pole}.  However, when extending
the problem to digital controller synthesis, many of these techniques lack
the ability to produce sound or stable results because they disregard the
effects of quantization and rounding.  Modern papers on
implementations/synthesis of LTI digital
controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretization,
failing to account for these error-inducing effects and can therefore result
in digitally unstable systems that have been proven to be robustly stable in
a continuous space.  This situation demands the inclusion of formal methods
to verify the effects of space discretization on the implementation of the
controller.

>>>>

The problem of parametric control synthesis based on stability measures for
continous Linear Time Invariant (LTI) Single Input-Single Output (SISO)
systems has been researched for several decades.  On a theoretical level it
is a solved problem~\cite{wonham1967pole} for which researches continuously
seek better results based on a number of properties in addition to
stability.  A vast range of pole placement techniques such as Moore's
algorithm for eigenstructure assignment~\cite{klein1977eigenvalue} or the
more recent Linear Quadratic Regulator (LQR)~\cite{bemporad2002explicit}
have been used in several studies with increasing degrees of succes to ensure
stability.  The latter approach highlights the importance of conserving
energy during the control process, which results in lower running costs.  
Since real systems are subject to tolerance and noise
as well as the need for economy, more recent studies focus on the problems of
achieving robust stability with minimum
gain~\cite{schmid2014unified,konigorski2012pole}.  However, when extending
the problem to digital controller synthesis, many of these techniques lack
the ability to produce sound or stable results because they disregard the
effects of quantization and rounding. Recent papers on
implementations/synthesis of LTI digital
controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretization,
failing to account for these error-inducing effects and can therefore result
in digitally unstable systems that have been proven to be robustly stable in
a continuous space.  This situation demands the inclusion of formal methods
to verify the effects of space discretization on the implementation of the
controller.
